---
title: "Data Analysis"
subtitle: "Summer Project"
date: "October 2, 2020"
author: "Gencer, Alper Sukru"
output: pdf_document
header-includes:
  - \usepackage{color}
  - \usepackage{float}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = T, fig.pos = 'H')
```

```{r loading packages, include=FALSE}
stopifnot(require("knitr"))
stopifnot(require("tidyverse"))
stopifnot(require("miscTools"))
stopifnot(require("gridExtra"))
stopifnot(require("corpcor"))
stopifnot(require("stargazer"))
stopifnot(require("vcov"))
stopifnot(require("faraway"))
stopifnot(require("lme4"))
stopifnot(require("latex2exp"))
stopifnot(require("jtools"))
```

\bigskip

# Data Analysis

Here, I run the analysis:

There are two questions that I try to answer:
\begin{enumerate}
  \item If the president's tweets show statistically different sentiment score before/after the issue date of executive order.
  \item If the reaction (likes/mentions) that president's tweets receives before/after the issue date of executive order are statistically different than the montly average. 
\end{enumerate}

```{r Q1 - getting ready, include=TRUE, warning = FALSE, message = FALSE}
rm(list = ls())
gencer_TrumpTweets_3 <- read_csv("C:/Users/alper/OneDrive/Belgeler/GitHub/python_summer2020/Summer_Project/gencer_TrumpTweets_3.csv")

####  There are some problems regarding python/R inconsistency. Let me correct them:
library(tidyverse)
gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  mutate(sentiment_bin = ifelse(
    sentiment_bin == "[[ True]]", 1, 0)
)
gencer_TrumpTweets_3[,ncol(gencer_TrumpTweets_3)-0] # Cool!
####  Let's correct the sentiment format:
gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  mutate(sentiment = gsub("\\[|\\]", "", sentiment))
gencer_TrumpTweets_3[,ncol(gencer_TrumpTweets_3)-1] # Cool!
gencer_TrumpTweets_3$sentiment <- as.numeric((gencer_TrumpTweets_3$sentiment))
```

\bigskip

Now let's find monthly like and retweet averages:

\bigskip

```{r Q2 - getting ready, include=TRUE, warning = FALSE, message = FALSE}
# Let's first correct the date format:
library(lubridate)
gencer_TrumpTweets_3$created_date2 <- as.Date((gencer_TrumpTweets_3$created_date), tryFormats = c("%m/%d/%Y"),)
gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  mutate(month = month(created_date2), year = year(created_date2))
gencer_TrumpTweets_3$monthyear <- paste(gencer_TrumpTweets_3$year, gencer_TrumpTweets_3$month, sep = "-")


gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  group_by(month, year) %>%
  # Monthly like and retweet averages:
  mutate(favorite_monthavrg = round(mean(favorite_count))) %>%
  mutate(retweet_monthavrg = round(mean(retweet_count))) %>%
  # Deviation from the Monthly like and retweet averages:
  mutate(diff_favorite = favorite_count - favorite_monthavrg) %>%
  mutate(diff_retweet = retweet_count - retweet_monthavrg)

```

And lastly, let's find monthly sentiment averages:


```{r Q3 - getting ready, include=TRUE, warning = FALSE, message = FALSE}
gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  group_by(month, year) %>%
  # Monthly like and retweet averages:
  mutate(sentiment_monthavrg = (mean(sentiment))) %>%
  mutate(sentiment_bin_monthavrg = (mean(sentiment_bin))) %>%
  # Deviation from the Monthly like and retweet averages:
  mutate(diff_sentiment = sentiment - sentiment_monthavrg) %>%
  mutate(diff_sentiment_bin = sentiment_bin - sentiment_bin_monthavrg)
```

\bigskip

## Hypothesis 1:

Let's check our first hypothesis that if the president's tweets show statistically different sentiment score close to the issue date of executive order:

```{r Q4a, include=TRUE, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE}
library(stargazer)
library(jtools)
library(scales)


gencer_TrumpTweets_3

```




```{r Q5, include=TRUE, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE, fig.cap = "DV = Sentiment", fig.show="hold", out.width="50%"}
library(stargazer)
library(jtools)

model_senti.1 <- lm(sentiment ~ int_1day , data = gencer_TrumpTweets_3)
model_senti.2 <- lm(sentiment ~ int_3day , data = gencer_TrumpTweets_3)
model_senti.3 <- lm(sentiment ~ int_5day , data = gencer_TrumpTweets_3)
model_senti.4 <- lm(sentiment ~ int_7day , data = gencer_TrumpTweets_3)
model_senti.5 <- lm(sentiment ~ int_11day , data = gencer_TrumpTweets_3)
model_senti.6 <- lm(sentiment ~ int_15day , data = gencer_TrumpTweets_3)

# stargazer(model_senti.1, model_senti.2, model_senti.3, model_senti.4, model_senti.5, model_senti.6, header=FALSE, type='latex')

plot_summs(model_senti.1, model_senti.2, model_senti.3, model_senti.4, model_senti.5, model_senti.6,
           scale = TRUE, model.names = c("1 Day Model", "3 Day Model", "5 Day Model", "7 Day Model", "11 Day Model", "15 Day Model"))
```


```{r Q6, include=TRUE, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE, fig.cap = "DV = Number of Likes", fig.show="hold", out.width="50%"}
library(stargazer)

model_likes.1 <- lm(favorite_count ~ int_1day , data = gencer_TrumpTweets_3)
model_likes.2 <- lm(favorite_count ~ int_3day , data = gencer_TrumpTweets_3)
model_likes.3 <- lm(favorite_count ~ int_5day , data = gencer_TrumpTweets_3)
model_likes.4 <- lm(favorite_count ~ int_7day , data = gencer_TrumpTweets_3)
model_likes.5 <- lm(favorite_count ~ int_11day , data = gencer_TrumpTweets_3)
model_likes.6 <- lm(favorite_count ~ int_15day , data = gencer_TrumpTweets_3)

# stargazer(model_likes.2, model_likes.3, model_likes.4, model_likes.5, model_likes.6, header=FALSE, type='latex')

plot_summs(model_likes.2, model_likes.3, model_likes.4, model_likes.5, model_likes.6, 
           scale = TRUE, model.names = c("3 Day Model", "5 Day Model", "7 Day Model", "11 Day Model", "15 Day Model"))
library(stargazer)

gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  mutate(favorite_count = log(favorite_count+ 0.001)) 

model_likes.1b <- lm(favorite_count ~ int_1day , data = gencer_TrumpTweets_3)
model_likes.2b <- lm(favorite_count ~ int_3day , data = gencer_TrumpTweets_3)
model_likes.3b <- lm(favorite_count ~ int_5day , data = gencer_TrumpTweets_3)
model_likes.4b <- lm(favorite_count ~ int_7day , data = gencer_TrumpTweets_3)
model_likes.5b <- lm(favorite_count ~ int_11day , data = gencer_TrumpTweets_3)
model_likes.6b <- lm(favorite_count ~ int_15day , data = gencer_TrumpTweets_3)

# stargazer(model_likes.2b, model_likes.3b, model_likes.4b, model_likes.5b, model_likes.6b, header=FALSE, type='latex')

plot_summs(model_likes.2b, model_likes.3b, model_likes.4b, model_likes.5b, model_likes.6b, 
           scale = TRUE, model.names = c("3 Day Model", "5 Day Model", "7 Day Model", "11 Day Model", "15 Day Model"))
```






```{r Q7, include=TRUE, warning = FALSE, message = FALSE, results = 'asis', echo = FALSE, fig.cap = "DV = Number of Retweets", fig.show="hold", out.width="50%"}
library(stargazer)

model_retweet.1 <- lm(retweet_count ~ int_1day , data = gencer_TrumpTweets_3)
model_retweet.2 <- lm(retweet_count ~ int_3day , data = gencer_TrumpTweets_3)
model_retweet.3 <- lm(retweet_count ~ int_5day , data = gencer_TrumpTweets_3)
model_retweet.4 <- lm(retweet_count ~ int_7day , data = gencer_TrumpTweets_3)
model_retweet.5 <- lm(retweet_count ~ int_11day , data = gencer_TrumpTweets_3)
model_retweet.6 <- lm(retweet_count ~ int_15day , data = gencer_TrumpTweets_3)

#stargazer(model_retweet.2, model_retweet.3, model_retweet.4, model_retweet.5, model_retweet.6, header=FALSE, type='latex')

plot_summs(model_retweet.2, model_retweet.3, model_retweet.4, model_retweet.5, model_retweet.6, 
           scale = TRUE, model.names = c("3 Day Model", "5 Day Model", "7 Day Model", "11 Day Model", "15 Day Model"))

library(stargazer)
gencer_TrumpTweets_3 <- gencer_TrumpTweets_3 %>%
  mutate(retweet_count = log(retweet_count+ 0.001)) 


model_retweet.1b <- lm(retweet_count ~ int_1day , data = gencer_TrumpTweets_3)
model_retweet.2b <- lm(retweet_count ~ int_3day , data = gencer_TrumpTweets_3)
model_retweet.3b <- lm(retweet_count ~ int_5day , data = gencer_TrumpTweets_3)
model_retweet.4b <- lm(retweet_count ~ int_7day , data = gencer_TrumpTweets_3)
model_retweet.5b <- lm(retweet_count ~ int_11day , data = gencer_TrumpTweets_3)
model_retweet.6b <- lm(retweet_count ~ int_15day , data = gencer_TrumpTweets_3)

#stargazer(model_retweet.2, model_retweet.3, model_retweet.4, model_retweet.5, model_retweet.6, header=FALSE, type='latex')

plot_summs(model_retweet.2b, model_retweet.3b, model_retweet.4b, model_retweet.5b, model_retweet.6b, 
           scale = TRUE, model.names = c("3 Day Model", "5 Day Model", "7 Day Model", "11 Day Model", "15 Day Model"))


```

